A Survey of Exoskeleton Control (Draft 1.1)

### 2015-09-17 paper.tex
more updates

\begin{verbatim}
 rigid
  gears
   planetary
   other
  harmonic drive
  ball screw
  cosine attachment
  Sarcos Primus Humanoid knee - to reduce moment arm variation with angle
 hydraulic/pneumatic circuit
 variable
  belts
  cones
  fluid
  adjustable moment arm
   linear slider
   XY slider for actuation and ``joint'' on foot.
\end{verbatim}

@@

@@

@@

>>>>

\begin{verbatim}
 rigid
  gears
   planetary
   other
  harmonic drive
  ball screw
  cosine attachment
  Sarcos Primus Humanoid knee - to reduce moment arm variation with angle
 hydraulic/pneumatic circuit
 variable
  belts
  cones
  fluid
  adjustable moment arm
   linear slider
   XY slider for actuation and ``joint'' on foot.
 series elastic actuation
\end{verbatim}

@@

Heat exhaust. Heatsink cooling, Force air colling, Water cooling.
Will housing and structure get too hot and fry operator?

@@

Often finite state machines whose states correspond to left stance, double support 1,
right stance, and double support 2 are used to select behaviors. Gait transitions
can be triggered by foot touchdown and liftoff events, or
displacement of the Center of Mass (CoM).

step-width adaptation algorithm

@@

Each of the powered joints has a series elastic
actuator, which can deliver 100 Nm torque and 1 kW power -> 10rad/s
IEEE TRANSACTIONS ON NEURAL SYSTEMS AND REHABILITATION ENGINEERING, VOL. 23, NO. 2, MARCH 2015 277-
Design and Control of the MINDWALKER
Exoskeleton
Shiqian Wang, Letian Wang, Cory Meijneke, Edwin van Asseldonk, Thomas Hoellinger, Guy Cheron,
Yuri Ivanenko, Valentina La Scaleia, Francesca Sylos-Labini, Marco Molinari, Federica Tamburella,
Iolanda Pisotta, Freygardur Thorsteinsson, Michel Ilzkovitz, Jeremi Gancet, Yashodhan Nevatia,
Ralf Hauffe, Frank Zanow, and Herman van der Kooij
